{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-01 bmvc_review.tex
Introduction Results Figure Added
Some More Edits in Introduction
All Sundays Work Included - Waiting for More Comments

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a KCF
is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient manner. 
In this paper, we use an ensemble of KCFs in turn, instead of running them all together on
every frame. By doing so, we could still address the scale change and
estimate target's motion efficiently while increasing run-time
performance. In particular, we deploy three KCF in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for Handling Large Motion} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty modified to track in low frame rate videos ($10$fps) dominated by large ego-motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on a UAV platform. Particle Filter can be deployed in case the camera motion is known. The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
\label{Workflow_figure_EnKCF}
\end{figure*}

\begin{figure*}[!t]
\centering
\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
\label{Workflow_figure_EnKCF2}
\end{figure*}

In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figure \ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those multiple KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change drastically. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

\begin{figure}[!t]
\centering
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
ROIs to $R_{t}^{L}$ and $R_{t}^{S}$. The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame. $R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area. Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.

>>>>

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a KCF
is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient manner. 
In this paper, we use an ensemble of KCFs in turn, instead of running them all together on
every frame. By doing so, we could still address the scale change and
estimate target's motion efficiently while increasing run-time
performance. In particular, we deploy three KCF in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Fig.~\ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
(a) \\
\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
(b)
\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker (a). It is slightly modified to handle extreme ego-motion
and we call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
\label{Workflows}
\end{figure}
The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflows}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for Handling Large Motion} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty modified to track in low frame rate videos ($10$fps) dominated by large ego-motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on a UAV platform. Particle Filter can be deployed in case the camera motion is known. The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF. The proposed framework can be seen in fig.~\ref{Workflows}.
%\begin{figure*}[!t]
%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
%\label{Workflow_figure_EnKCF}
%\end{figure*}
%\begin{figure*}[!h]
%\centering
%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
%\label{Workflow_figure_EnKCF2}
%\end{figure*}

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
 many variation of KCF were investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those multiple KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change drastically. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. This fact can be visualized in fig.~\ref{fig:Filters_Comparison}.
By alternating three KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{The video frame and the learned scale correlation filters are shown next to it. 
The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
Filters updated every five frame and every frame display very large correlation.}
\label{fig:Filters_Comparison}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
ROIs to $R_{t}^{L}$ and $R_{t}^{S}$. The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame. $R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area. Fig.~\ref{Workflows} illustrates the workflow of the
proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.
